\LARGE \bf A Teachable Robotic Agent for Children Learning Handwriting, Capable of Simulated Handwriting Itself

### 2014-11-27 rebuttal_sorted.txt

We agree with the points raised: it is a limitation of the question, which we imposed ourselves to avoid putting words in the children's mouths if we were to ask directly if the robot's writing was believable. Our argument is that at no point in the interaction did any child express that they did not believe that the robot was writing itself, even in a situation where they could have said "well, it's not *really* writing". We accept that we cannot conclude that the children believed it was writing, and will reword the outcome to instead be that no child ever expressed that they did not believe it was writing.

>    (3) “For example, for the model shown in Figure 1, the parameters may
>    represent the height of the top half of the letter compared to the bottom
>    half, the width of the overall shape, etc. Consequently, the shape
>    modelling process has produced the desired outcomes of parameterising the
>    shapes in ways which are able to be used to deform them meaningfully.”
>    - The author’s subjective appraisal of what variations are captured by
>    PCA is insufficient to claim the the deformations are meaningful.
>    Further, the word “meaningful” lacks grounding (what exactly does it
>    mean here)?
DONE
The deformations are meaningful in the sense that if a teacher wishes to create initial letters with a particular feature (a 'd' with a large loop, for example), it is possible with this system. We will clarify that it is the ability to create varied levels of deformations which may be ascribed descriptive interpretations (not just numerical) that is the desired outcome.

>    Additionally, more information is needed about the evaluation. How was
>    the initial parameter vector for a letter drawn? 
DONE

>    With what wording were
>    children asked whether they believed “the robot was learning and that
>    they were the ones teaching it”?

@@

We agree with each of the points made; they will be addressed.

>    The work is very sound, although it's unclear which parts of the shape
>    modeling algorithm are novel.  This review is written under the
>    assumption that the idea of shape modeling is not novel, but that using
>    the model to generate "bad" examples is.  Otherwise, the system design
>    and evaluation are excellent.
DONE
This is accurate and will be clarified in the section on the shape modeling algorithm.

### 2014-11-27 main.tex
R1 initial parameters
R1 abstract 'context of robotics outside coding' concern

Preliminary in situ studies have been conducted with primary school classes to obtain
insight into children's use of the novel system. 
%The technical components of the system have been validated, in that children 
Children aged 6-8 were successfully led to believe that the robot was
actually writing on the tablet, and were able to improve the robot's writing to a
level which they were satisfied with, validating the interaction.

Furthermore, the system represents a
significant step towards an innovative use for robotics which addresses a
wide-spread and socially meaningful challenge in education, and provides context
for robotics in education beyond the well-explored use of teaching coding and
robotics-related subjects.

@@

The study at the second school involved 21 french-speaking students aged 7-8 years: 7 children
interacted with the robot individually and 7 sessions included the remaining
14 students interacting with the robot in pairs. The duration of the sessions
was between 8 and 15 minutes, with an average of 11.4 minutes (SD = 2.3). % * <deanna.m.hood@gmail.com> 2014-09-05T09:25:41.865Z:
%
% We prompted them when time was short, didn't we? Or did they just say test
% whenever they wanted to...
%

>>>>

Preliminary in situ studies have been conducted with primary school classes to obtain
insight into children's use of the novel system. 
Children aged 6-8 were successfully able to engage with the robot and to improve its 
writing to a level which they were satisfied with. The validation of the interaction
represents a significant step towards an innovative use for robotics which addresses a
widespread and socially meaningful challenge in education.

%, and provides context
%for robotics in education beyond the well-explored use of teaching coding and
%robotics-related subjects.

@@

The study at the second school involved 21 french-speaking students aged 7-8 years: 7 children
interacted with the robot individually and 7 sessions included the remaining
14 students interacting with the robot in pairs. The duration of the sessions
was between 8 and 15 minutes, with an average of 11.4 minutes (SD = 2.3). 
Initial parameters were drawn from a range purposely chosen to generate shapes 
for letters 'e' and 's' which would elicit correction. For the other letters, 
parameters were fixed, generating shapes which some groups chose to correct 
(e.g. 13/14 for 'n' and 2/14 for 'c').
